Self Regulation Ontology Retest Analyses

### 2018-08-09 code/SRO_Retest_Analyses.Rmd
updating intrameasure trial num analyses

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))

@@

```{r eval=FALSE}
hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))

hr_merge = hr_merge %>%
  gather(key, value, -sub_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))

@@

trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
                              acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              avg_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              std_rt_error_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              std_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              missed_percent_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              cue_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              cue_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              task_switch_cost_rt_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              task_switch_cost_rt_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              cue_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              cue_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              task_switch_cost_acc_100_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              task_switch_cost_acc_900_icc=rep(NA, length(unique(t1_dvs$breaks))))

for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_error_icc[i] = get_icc("avg_rt_error", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$std_rt_error_icc[i] = get_icc("std_rt_error", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$std_rt_icc[i] = get_icc("std_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$missed_percent_icc[i] = get_icc("missed_percent", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$cue_switch_cost_rt_100_icc[i] = get_icc("cue_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$cue_switch_cost_rt_900_icc[i] = get_icc("cue_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$trial_switch_cost_rt_100_icc[i] = get_icc("task_switch_cost_rt_100", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$trial_switch_cost_rt_900_icc[i] = get_icc("task_switch_cost_rt_900", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$cue_switch_cost_acc_100_icc[i] = get_icc("cue_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$cue_switch_cost_acc_900_icc[i] = get_icc("cue_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$trial_switch_cost_acc_100_icc[i] = get_icc("task_switch_cost_acc_100", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$trial_switch_cost_acc_900_icc[i] = get_icc("task_switch_cost_acc_900", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

@@

trial_num_rel_df %>%
  select(-std_rt_icc, -std_rt_error_icc)%>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "avg_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "Average RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_color_manual(values = cols,
                     breaks = c("Average RT correct", "Average RT error", "Cue switch cost RT (100)","Cue switch cost RT (900)", "Task switch cost RT (100)","Task switch cost RT (900)","Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)",  "Task switch cost Acc (100)",  "Task switch cost Acc (900)"))+
  ylim(-1,1)+
  guides(color = guide_legend(ncol=2, byrow=F))

ggsave('Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```

>>>>

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_shift_dvs.csv'))
t2_dvs = read.csv(paste0(retest_data_path, 't2_shift_dvs.csv'))

@@

```{r eval=FALSE}
hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "level_1"))

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -level_1) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))%>%
  rename(sub_id = worker_id,
         breaks = level_1)

@@

'acc', 'avg_rt', 'conceptual_responses', 'fail_to_maintain_set',
       'learning_rate', 'learning_to_learn', 'nonperseverative_errors',
       'perseverative_errors', 'perseverative_responses', 'total_errors'

trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
                              acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              conceptual_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              fail_to_maintain_set_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              learning_rate_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              learning_to_learn_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              nonperseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              perseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              perseverative_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              total_errors_icc=rep(NA, length(unique(t1_dvs$breaks))))

for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$conceptual_responses_icc[i] = get_icc("conceptual_responses", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$fail_to_maintain_set_icc[i] = get_icc("fail_to_maintain_set", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$learning_rate_icc[i] = get_icc("learning_rate", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$learning_to_learn_icc[i] = get_icc("learning_to_learn", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$nonperseverative_errors_icc[i] = get_icc("nonperseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$perseverative_errors_icc[i] = get_icc("perseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$perseverative_responses_icc[i] = get_icc("perseverative_responses", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$total_errors_icc[i] = get_icc("total_errors", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks, value, color=key))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  ylim(-1,1)

ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```
